### 2022-11-11 doc/paper.tex
set up documentation

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2021

% ready for submission
\usepackage[preprint]{neurips_2021}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2021}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2021}

% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{neurips_2021}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[colorlinks = true, 
		    linkcolor = blue,
		    urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}       
% hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{natbib}
\usepackage[pdftex]{graphicx}
\usepackage{siunitx} % Required for alignment
\sisetup{
  round-mode          = places, % Rounds numbers
  round-precision     = 2, % to 2 places
}

\bibliographystyle{unsrtnat}

\title{Can language models be used to predict dependencies between knowledge components?}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  Dominik Glandorf\\
  Matrikelnummer 6007407\\
  \texttt{dominik.glandorf@student.uni-tuebingen.de} \\
  \And
  Anastasiia Alekseeva\\
  Matrikelnummer 6001480\\
  \texttt{anastasiia.alekseeva@student.uni-tuebingen.de} \\
  \\
  GitHub repository: \url{https://github.com/dominikglandorf/learning-dependencies}
}

\begin{document}
\vspace*{-5mm}
\maketitle
\vspace*{-5mm}

\begin{abstract}
% What did we do?

% Why did we to it? What did we expect?

% How did we do it?

% What did we find out?

% What now?

\end{abstract}

\section{Introduction}
%% Why are we interested in learning dependencies?
% Problem of instructional sequencing: 
% Definition KCs
% Possible solution inference from user behavior (SOURCE) but has the disadvantage of disengaging users with mastered KCs or KCs that require further prerequisites (SOURCE about ZPD)
% Assumption: information about dependencies between KCs makes instructional sequencing more effective in terms of learning
% Definition: KC dependency (SOURCE)

% What can we contribute?
% 1. Extract KC dependencies from textbooks
% 2. Bypass textbook mining by querying a pre-trained language model to disclose relationships between KCs

% What is our research question?
% How well can langauge models predict dependencies between Knowledge Components compared to textbooks?

% Related work
% Field: Dependencies between Knowledge Components
% of interest: How are dependencies conceptualized?
% Field: Textbook Knowledge Extraction
% of interest: How are relationships betweens KCs extracted?
% Field: Prompt Engineering
% of interest: How can we get internal representations out of a language model?

\section{Method}

\subsection{Information sources}
% Where did we get the data from?
% textbooks
% language models

\subsection{Structured information extraction}
% Data quality

% Visualizations

% Statistics

\section{Results}

\section{Discussion}
% What is our main result?

% What could be potential flaws?

% Q: Outlook and Future research ideas:%

\bibliography{references.bib}

\end{document}

### 2022-11-12 doc/paper.tex
extend paper

@@
 %% Why are we interested in learning dependencies?
-% Problem of instructional sequencing: 
+% Problem of sequencing in Instructional Design:
+Effective and efficient instruction does not only incorporate \textit{what} to teach but also \textit{how} to teach.
+Models of instructional design especially emphasize the importance of order of instruction.
+More precisely, prerequisites of educational content should be taught first (Morrison et al, 2019).
 % Definition KCs
-% Possible solution inference from user behavior (SOURCE) but has the disadvantage of disengaging users with mastered KCs or KCs that require further prerequisites (SOURCE about ZPD)
-% Assumption: information about dependencies between KCs makes instructional sequencing more effective in terms of learning
-% Definition: KC dependency (SOURCE)
+However, a definition of what has to be sequenced is necessary before.
+Merill (1983) differentiated learning objectives such as facts, concepts, principles, rules, procedures, interpersonal skills and attitudes as well as their sole recall from their application.
+In this work we will focus on concepts and their relations.
+% Learning dependency
+% Assumption: information about dependencies between concepts makes instructional sequencing more effective in terms of learning
+If one concept is a prerequisite of another, we call this relation a learning dependency.
+For example, to understand the concept of a derivative the concept of a function is a prerequisite that will facilitate or even enable learning.
+When the dependencies are thought of as directed edges between nodes that represent concepts, a learning dependency graph emerges which is a special type of a knowledge graph (Wang et al 2016).
+This graph is also called \textit{concept map} in the field of Learning Sciences.
+% Mining of learning dependencies
+Theoretically, prerequisites can be inferred from learner behavior by testing their performance after being presented different instructional sequences.
+However, this has the disadvantage of disengaging users with too difficult concepts before teaching easier or necessary ones.
+Experts usually dispose of the required knowledge about concepts to create concept maps.
+The high cost of expert knowledge motivates the automatic mining of learning dependencies from appropriate sources which is the core problem of this work.
 
@@
 % Related work
-% Field: Dependencies between Knowledge Components
+% Field: Dependencies between concepts
 % of interest: How are dependencies conceptualized?

### 2022-11-21 doc/paper.tex
expand introduction

@@
 
-\title{Can language models be used to predict dependencies between knowledge components?}
+\title{Can language models be used to predict educational concept dependencies?}
 
@@
 % Definition KCs
-However, a definition of what has to be sequenced is necessary before.
-Merill (1983) differentiated learning objectives such as facts, concepts, principles, rules, procedures, interpersonal skills and attitudes as well as their sole recall from their application.
+As potential contents, Merill (1983) differentiated learning objectives such as facts, concepts, principles, rules, procedures, interpersonal skills and attitudes as well as their sole recall from their application.
 In this work we will focus on concepts and their relations.
@@
 If one concept is a prerequisite of another, we call this relation a learning dependency.
-For example, to understand the concept of a derivative the concept of a function is a prerequisite that will facilitate or even enable learning.
+For example, to understand the concept of a derivative knowledge about the concept of a function before will facilitate or even enable learning.
 When the dependencies are thought of as directed edges between nodes that represent concepts, a learning dependency graph emerges which is a special type of a knowledge graph (Wang et al 2016).
@@
 % Mining of learning dependencies
-Theoretically, prerequisites can be inferred from learner behavior by testing their performance after being presented different instructional sequences.
+Prerequisites can be inferred from learner behavior by testing their performance after being presented different instructional sequences (Pavlik et al., 2008, Vuong et al., 2011).
 However, this has the disadvantage of disengaging users with too difficult concepts before teaching easier or necessary ones.
@@
 
+% Advantage: Curriculum planning (Yang, 2015), Automated Assessment (Wang 2015)
+
 % What can we contribute?
 % 1. Extract KC dependencies from textbooks
-% 2. Bypass textbook mining by querying a pre-trained language model to disclose relationships between KCs
+% 2. Bypass textbook mining by querying a pre-trained language model to disclose relationships between concepts
 
@@
 
-% Related work
+\subsection{Related work}
 % Field: Dependencies between concepts
 % of interest: How are dependencies conceptualized?
+Talukdar and Cohen (2012) defined the prerequisite relation in terms of the consumption of information about concepts.
+Vuong (2011) if a better graduation rate given prerequisite knowledge is fulfilled.
+Concepts are often equated with Wikipedia articles (Talukdar and Cohen, 2015; Wang, 2015).
 % Field: Textbook Knowledge Extraction
-% of interest: How are relationships betweens KCs extracted?
+% of interest: How are relationships betweens concepts extracted?
 % Field: Prompt Engineering

### 2022-11-23 src/wikifier.py
wikified whole book

@@ -1,0 +1,26 @@
+import requests
+from dotenv import dotenv_values
+config = dotenv_values("../.env")
+userKey = config['WIKIFIER_USER_KEY']
+
+def get_annotations(text, offset=0):
+    print(offset)
+    try:
+        response = requests.post("http://www.wikifier.org/annotate-article",
+            data={"userKey": userKey,
+                "lang": "en",
+                "text": text,
+                "support": "true",
+                "ranges": "true"},
+        )
+        response = response.json()
+
+        for a in response['annotations']:
+            for s in a['support']:
+                s['chFrom'] += offset
+                s['chTo'] += offset
+
+        return response['annotations']
+    except Exception:
+        print(Exception)
+        return []

### 2022-12-01 doc/paper.tex
wikified whole book
add exp 10

@@
 Models of instructional design especially emphasize the importance of order of instruction.
-More precisely, prerequisites of educational content should be taught first (Morrison et al, 2019).
+More precisely, prerequisites of educational content should be taught first \citep{morrison2019designing}.
 % Definition KCs
@@
 For example, to understand the concept of a derivative knowledge about the concept of a function before will facilitate or even enable learning.
-When the dependencies are thought of as directed edges between nodes that represent concepts, a learning dependency graph emerges which is a special type of a knowledge graph (Wang et al 2016).
+When the dependencies are thought of as directed edges between nodes that represent concepts, a learning dependency graph emerges which is a special type of a knowledge graph \citep{wang2016using}.
 This graph is also called \textit{concept map} in the field of Learning Sciences.
@@
 
-% Advantage: Curriculum planning (Yang, 2015), Automated Assessment (Wang 2015)
+% Advantage: Curriculum planning (Yang, 2015) especially for new topics, Automated Assessment (Wang 2015)
 
@@
 % What is our research question?
-% How well can langauge models predict dependencies between Knowledge Components compared to textbooks?
+% How well can langauge models predict dependencies between key concepts compared to expert knowledge in textbooks?
 
@@
 % of interest: How are dependencies conceptualized?
-Talukdar and Cohen (2012) defined the prerequisite relation in terms of the consumption of information about concepts.
+\cite{talukdar2012crowdsourced} defined the prerequisite relation in terms of the consumption of information about concepts.
 Vuong (2011) if a better graduation rate given prerequisite knowledge is fulfilled.
-Concepts are often equated with Wikipedia articles (Talukdar and Cohen, 2015; Wang, 2015).
+Concepts are often equated with Wikipedia articles (Talukdar and Cohen, 2012; Wang, 2015).
 % Field: Textbook Knowledge Extraction
@@
 % textbooks
+For preprocessing the textbooks we used Wikifier \citep{brank2017annotating}.
 % language models

### 2022-12-03 exp/12_AsyncRequest.py
add asynch requests

@@ -1,0 +1,61 @@
+import aiohttp
+import asyncio
+import time
+import pandas as pd
+import numpy as np
+import unicodedata
+import pickle
+
+from dotenv import dotenv_values
+config = dotenv_values("../.env")
+userKey = config['WIKIFIER_USER_KEY']
+
+start_time = time.time()
+batch_size = 5000
+next_delay = 7
+
+async def get_annos(session, url, text, offset):
+    global next_delay
+    next_delay += delay
+    await asyncio.sleep(next_delay)
+    print(offset)
+    data={"userKey": userKey,
+                "lang": "en",
+                "text": text,
+                "support": "true",
+                "ranges": "true"}
+           
+    async with session.post(url, data=data) as response:
+        print(response.status)
+        try:
+            annos = await response.json()
+            for a in annos['annotations']:
+                for s in a['support']:
+                    s['chFrom'] += offset
+                    s['chTo'] += offset
+            print("Received "+ str(offset))
+            return annos['annotations']
+        except Exception as e:
+            print("Error in "+ str(offset))
+            print(str(e))
+            return []
+        
+
+async def main(text):
+    async with aiohttp.ClientSession() as session:
+        tasks = []
+        batches = int(np.floor(len(text)/batch_size))
+        for i in range(batches):
+            url = f'http://www.wikifier.org/annotate-article'
+            tasks.append(asyncio.ensure_future(get_annos(session, url, text[i*batch_size:(i+1)*batch_size], i*batch_size)))
+        annos = await asyncio.gather(*tasks)
+        file = open("../dat/annotations/Beezer_First_Course.pkl", 'wb')
+        pickle.dump([item for sublist in annos for item in sublist], file)
+        file.close()
+
+delay = 7
+data = pd.read_json("../dat/parsed_books/parsed_books.json")
+text = unicodedata.normalize("NFKD", " ".join(data.pages[0]))
+#print(text)
+asyncio.run(main(text))
+print("--- %s seconds ---" % (time.time() - start_time))

### 2023-03-01 doc/paper.tex
Update paper.tex
update paper draft

@@
 
-\title{Can language models be used to predict educational concept dependencies?}
+\title{Extracting and evaluating educational concept dependencies implicit in Large Language Models}
 
@@
   Anastasiia Alekseeva\\
-  Matrikelnummer 6001480\\
+  Matrikelnummer 5994775\\
   \texttt{anastasiia.alekseeva@student.uni-tuebingen.de} \\
   \\
-  GitHub repository: \url{https://github.com/dominikglandorf/learning-dependencies}
+  GitHub repository: \url{https://github.com/mlcolab/learning-dependencies}
 }
@@
 \section{Introduction}
-%% Why are we interested in learning dependencies?
-% Problem of sequencing in Instructional Design:
-Effective and efficient instruction does not only incorporate \textit{what} to teach but also \textit{how} to teach.
-Models of instructional design especially emphasize the importance of order of instruction.
-More precisely, prerequisites of educational content should be taught first \citep{morrison2019designing}.
-% Definition KCs
-As potential contents, Merill (1983) differentiated learning objectives such as facts, concepts, principles, rules, procedures, interpersonal skills and attitudes as well as their sole recall from their application.
-In this work we will focus on concepts and their relations.
-% Learning dependency
+% What is the field where we contributed
+Large Language Models are trained on immense corpora of text and have proven to capture included factual information by building on it when performing well in downstream tasks such as question answering.
+This observation led to the research line of Knowledge Extraction from LLMs (Cohen, 2023).
+In this work, we focus on the extraction of educational knowledge that is implicitly captured in LLMs and poses a subfield that has rather stagnated in the previous years.
+
+% Why are we interested in concept dependencies?
+%% Problem of sequencing in Instructional Design:
+Effective and efficient instruction does not only incorporate what to teach but also how to teach.
+Guidelines for \textit{instructional sequencing} emphasize the order of instruction.
+More precisely, prerequisites of educational content should be either known to the student or taught first \citep{morrison2019designing}.
+% Definition concepts
+Within educational content, Merill (1983) differentiated facts, concepts, principles, rules, procedures, interpersonal skills, attitudes, and their sole recall from their application.
+To simplify, we will focus on concepts and their relations.
+% Concept dependency
 % Assumption: information about dependencies between concepts makes instructional sequencing more effective in terms of learning
-If one concept is a prerequisite of another, we call this relation a learning dependency.
-For example, to understand the concept of a derivative knowledge about the concept of a function before will facilitate or even enable learning.
-When the dependencies are thought of as directed edges between nodes that represent concepts, a learning dependency graph emerges which is a special type of a knowledge graph \citep{wang2016using}.
+If one concept is a prerequisite of another, we call this relation a concept dependency.
+For example, to understand the concept of a derivative, having knowledge about the concept of a function will facilitate or even enable learning.
+When the dependencies are thought of as directed edges between nodes that represent concepts, a concept dependency graph emerges which is a special type of a knowledge graph \citep{wang2016using}.
 This graph is also called \textit{concept map} in the field of Learning Sciences.
-% Mining of learning dependencies
+
+% Approaches: Automatic extraction of concept dependencies
 Prerequisites can be inferred from learner behavior by testing their performance after being presented different instructional sequences (Pavlik et al., 2008, Vuong et al., 2011).
@@
 Experts usually dispose of the required knowledge about concepts to create concept maps.
-The high cost of expert knowledge motivates the automatic mining of learning dependencies from appropriate sources which is the core problem of this work.
+The high cost of expert knowledge motivates the automated extraction of concept dependencies from appropriate sources.
 
-% Advantage: Curriculum planning (Yang, 2015) especially for new topics, Automated Assessment (Wang 2015)
+% What is our research question?
+% How to extract educational concept dependencies that are implicit and evaluate them using existing knowledge media?
 
 % What can we contribute?
-% 1. Extract KC dependencies from textbooks
-% 2. Bypass textbook mining by querying a pre-trained language model to disclose relationships between concepts
-
-% What is our research question?
-% How well can langauge models predict dependencies between key concepts compared to expert knowledge in textbooks?
+% 1. No benchmark available -> we set up an evaluation framework based on textbooks and Wikipedia
+% 2. Emerging field of prompt engineering -> we engineered a simple but effective prompt process to query a LLM
 

### 2023-03-02 doc/paper.tex
paper outline

@@
 
-\title{Extracting and evaluating educational concept dependencies implicit in Large Language Models}
+\title{Extracting and evaluating educational concept dependencies from Large Language Models}
 
@@
 \section{Introduction}
-% What is the field where we contributed
-Large Language Models are trained on immense corpora of text and have proven to capture included factual information by building on it when performing well in downstream tasks such as question answering.
-This observation led to the research line of Knowledge Extraction from LLMs (Cohen, 2023).
-In this work, we focus on the extraction of educational knowledge that is implicitly captured in LLMs and poses a subfield that has rather stagnated in the previous years.
+% Starting broad
+% Field of contribution
+Large Language Models (LLMs) are trained on immense corpora of text and have proven to build on embedded factual information when performing well in downstream tasks such as question answering.
+Accessing this knowledge, which is represented by billions of parameters and the network's architecture, has given rise to the research field of Knowledge Extraction from LLMs (Cohen, 2023).
+Computer-assisted education could greatly benefit from making implicit educational knowledge in LLMs accessible.
+This creates new perspectives for a subfield of knowledge engineering that has rather stagnated in the previous years.
 
-% Why are we interested in concept dependencies?
+% What kind of information do we want to extract?
 %% Problem of sequencing in Instructional Design:
+Concept dependencies are complex but highly relevant educational knowledge.
 Effective and efficient instruction does not only incorporate what to teach but also how to teach.
@@
 Within educational content, Merill (1983) differentiated facts, concepts, principles, rules, procedures, interpersonal skills, attitudes, and their sole recall from their application.
-To simplify, we will focus on concepts and their relations.
+To simplify, we will focus on concepts and their relations defined understanding.
 % Concept dependency
 % Assumption: information about dependencies between concepts makes instructional sequencing more effective in terms of learning
-If one concept is a prerequisite of another, we call this relation a concept dependency.
+If one concept is a prerequisite of another, we refer to this relation as a concept dependency.
 For example, to understand the concept of a derivative, having knowledge about the concept of a function will facilitate or even enable learning.
@@
 This graph is also called \textit{concept map} in the field of Learning Sciences.
+% TODO: provide a (graphical) example of a small concept map
+% Why is is important?
+The graph can be used to advance curriculum planning (Yang, 2015), especially for new topics that might not be covered in textbooks or automated assessment (Wang, 2015).
 
-% Approaches: Automatic extraction of concept dependencies
+% What is the gap in research that we tackle?
+% What is our research question?
+% How to extract educational concept dependencies that are implicit and evaluate them using existing knowledge media?
+In this work, we tackled the question how to extract this particular knowledge graph and how to evaluate its quality in a scalable manner.
+
+% What can we contribute?
+% 1. No benchmark available -> we set up an evaluation framework based on textbooks and Wikipedia
+First, there was no classical benchmark available to evaluate the accuracy of extracted information.
+Therefore, we propose a set of methods to use existing unstructured knowledge sources, namely Wikipedia and textbooks, to create baselines for evaluation.
+Due to the heuristic character of these methods, we conducted a manual assessment to test their suitability for our purpose.
+The resulting dataset can be used as a human baseline for further research.
+
+% 2. Emerging field of prompt engineering -> we engineered a simple but effective prompt process to query a LLM
+Second, there is no established manner to extract the desired knowledge from the LLM.
+The emerging field of prompt engineering is currently a vast collection of commands to query LLMs.
+We propose a method called output refeeding that sequentially queries the language generation model and transforms its answers into a knowledge graph.
+
+\subsection{Related work}
+% Field: Concept Dependency Extraction
+% of interest: How are concept dependencies defined?
+\cite{talukdar2012crowdsourced} defined the prerequisite relation in terms of the consumption of information about concepts.
+Vuong (2011) if a better graduation rate given prerequisite knowledge is fulfilled.
+Concepts are often equated with Wikipedia articles (Talukdar and Cohen, 2012; Wang, 2015).
+
+% Other approaches: Learning Path Analysis and Expert Knowledge
 Prerequisites can be inferred from learner behavior by testing their performance after being presented different instructional sequences (Pavlik et al., 2008, Vuong et al., 2011).
@@
 
-% What is our research question?
-% How to extract educational concept dependencies that are implicit and evaluate them using existing knowledge media?
-
-% What can we contribute?
-% 1. No benchmark available -> we set up an evaluation framework based on textbooks and Wikipedia
-% 2. Emerging field of prompt engineering -> we engineered a simple but effective prompt process to query a LLM
-
-\subsection{Related work}
-% Field: Dependencies between concepts
-% of interest: How are dependencies conceptualized?
-\cite{talukdar2012crowdsourced} defined the prerequisite relation in terms of the consumption of information about concepts.
-Vuong (2011) if a better graduation rate given prerequisite knowledge is fulfilled.
-Concepts are often equated with Wikipedia articles (Talukdar and Cohen, 2012; Wang, 2015).
 % Field: Textbook Knowledge Extraction
 % of interest: How are relationships betweens concepts extracted?
-% Field: Prompt Engineering
+
+% Field: Prompt Engineering for Knowledge Graph creation
 % of interest: How can we get internal representations out of a language model?
+% Cohen, 2023
+% GraphGPT
 
 \section{Method}
+% Section summary
+In this section, we will first detail our research design and then the characteristics of our information sources as well as the methods that we used to produce the knowledge graph.
 
-\subsection{Information sources}
-% Where did we get the data from?
-% textbooks
+\subsection{Research design} 
+% two baseline methods: textbooks and Wikipedia
+% information extraction: one LLM method
+% evaluation
+% 1. manual inspection via DashBoard
+% 2. manual labeling
+% 3. convergence between LLM and baselines
+
+\subsection{Baseline extraction}
+\subsubsection{Wikipedia}
+% Why Wikipedia?
+% good coverage according to one of our papers
+% 1462 unique articles for book index entries, these were covered in the textbooks (we had to select a subset of concepts to reduce computational effort)
+% How did we get the information?
+% describe Algorithm to extract dependencies:
+%• Assumption: understanding the concept’s definition in Wikipedia requires understanding the concepts in it
+%• Operationalization: links to other articles in the first sentence of article
+%• Filtered out links to fields (“Mathematics”), persons (“Gabriel Cramer), and concepts that linked even earlier to the concept of interest
+
+\subsubsection{Textbooks}
+% Types of textbooks (why linear algebra?)
+
+% Amount of data
+% 10 books on Linear Algebra
+% 584 pages on average (652,297 characters)
+% 382 number of index entries (median)
+
+% Steps of processing
+% preprocessing
+% entity recognition and disambigation
+% Wikifier: identify entity mentions using link targets and PageRank
 For preprocessing the textbooks we used Wikifier \citep{brank2017annotating}.
-% language models
+% Wikisearch: query Wikipedia search engine for keyword (and field) and rank results based on Levenshtein distance
 
-\subsection{Structured information extraction}
-% Data quality
+% relation extraction
+% common introductory usage: identify other concepts that are most often mentioned on the first page given in the index across all books
+% order pruning:  identify unlikely dependencies based on a certain number of books that introduce concepts in a particular order
 
-% Visualizations
+\subsection{LLM extraction}
+% description of T0PP and our infrastructure
+% • Fine-tuned BLOOM on several question-answering datasets
+% • 11 billion parameters (44GB RAM) • ~3-10 seconds per request on our infrastructure
 
-% Statistics
+% description of extraction procedure
+% 1. output refeeding
+% first prompt: {definition} := What is the mathematical definition of {concept}?
+% second prompt:  {list of dependencies} := What mathematics concepts are mentioned here: {definition}
+% 2. response parsing to Wikipedia article
+% {canonical list of dependencies} :=Wikisearch disambiguation on {list of dependencies}
+
+\subsection{Manual inspection via Dashboard}
+%
+
+\subsection{Manual baseline}
+% procedure to assess the accuracy of output
+
+\subsection{Convergence statistics}
+% for which concepts did we compare what to see what
 
 \section{Results}
+% Case Study using Dashboard
+
+%Manual baseline
+% Interrater reliability
+% How good are the baselines?
+% How good is the LLM?
+% diagram
+
+%Convergence statistics
+% diagram for similarity of outputs
 
@@
 % What is our main result?
+% we are able to make the implicit knowledge explicit far above chance level
+% problem is very complex -> humans do not fully agree
+% Wikipedia might be the best source to automatically evaluate the output
 
-% What could be potential flaws?
+% What are potential flaws?
+% disambiguation already includes noise
+% we only evaluated up to two levels of the graph, not the graph as a whole. different level of abstractions in extracted dependencies
+% is there even something like a gold standard? some educational reflection about different didactic approaches and more depth than just understanding the definition of a topic
+% we are still using the language generator, so it is just another downstream task, maybe it is more of a philosophical question what is implicit/explicit knowledge
 
-% Q: Outlook and Future research ideas:%
+% Q: Outlook and Future research ideas:
+% advancements in LLMs that are interesting for us
+% use cases in education
 

### 2023-03-07 doc/paper.tex
Added graphs to paper

@@
 % \usepackage[nonatbib]{neurips_2021}
-
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
 % hyperlinks
+\usepackage{float}
 \usepackage{url}            % simple URL typesetting
@@
 Large Language Models (LLMs) are trained on immense corpora of text and have proven to build on embedded factual information when performing well in downstream tasks such as question answering.
-Accessing this knowledge, which is represented by billions of parameters and the network's architecture, has given rise to the research field of Knowledge Extraction from LLMs (Cohen, 2023).
-Computer-assisted education could greatly benefit from making implicit educational knowledge in LLMs accessible.
-This creates new perspectives for a subfield of knowledge engineering that has rather stagnated in the previous years.
+Accessing this knowledge, which is represented by billions of parameters and the network's architecture, has given rise to the research field of Knowledge Extraction from LLMs (\cite{cohen2023crawling}), which rests on the assumption that the language models can help retrieve information on the relation between entities.
+
+This work tries to contribute to the research field and to answer the question of whether general LLMs are able to provide a valid dependency structure of educational concepts.
+To find the answer to the research question, we are going to solve two main subtasks: 1) extraction of implicit educational concept dependencies, and 2) evaluation of the retrieved dependencies or the resulting graphs by existing knowledge media.
+
+Apart from the field of knowledge extraction from LLMs, which is a subfield of computational linguistics, our work may contribute to applied education sciences by improving computer-assisted education and creating new perspectives for a subfield of knowledge engineering that has rather stagnated in the previous years.
 
@@
 %% Problem of sequencing in Instructional Design:
-Concept dependencies are complex but highly relevant educational knowledge.
-Effective and efficient instruction does not only incorporate what to teach but also how to teach.
-Guidelines for \textit{instructional sequencing} emphasize the order of instruction.
-More precisely, prerequisites of educational content should be either known to the student or taught first \citep{morrison2019designing}.
+In particular, effective and efficient instruction does not only incorporate what to teach but also how to teach, especially the order of instruction.
+It is proven that \textit{instructional sequencing} enhances the process of learning when prerequisites of educational content are known to the student or taught first \citep{morrison2019designing}.
 % Definition concepts
 Within educational content, Merill (1983) differentiated facts, concepts, principles, rules, procedures, interpersonal skills, attitudes, and their sole recall from their application.
-To simplify, we will focus on concepts and their relations defined understanding.
+We will focus on concepts and their relations defined understanding.
 % Concept dependency
 % Assumption: information about dependencies between concepts makes instructional sequencing more effective in terms of learning
-If one concept is a prerequisite of another, we refer to this relation as a concept dependency.
+
+To be more precise, if one concept is a prerequisite of another, we refer to this relation as a concept dependency.
 For example, to understand the concept of a derivative, having knowledge about the concept of a function will facilitate or even enable learning.
@@
 % Why is is important?
-The graph can be used to advance curriculum planning (Yang, 2015), especially for new topics that might not be covered in textbooks or automated assessment (Wang, 2015).
+The graph can be used to advance curriculum planning (\cite{yang2015concept}), especially for new topics that might not be covered in textbooks or automated assessment (Wang, 2015).
 
@@
 % How to extract educational concept dependencies that are implicit and evaluate them using existing knowledge media?
-In this work, we tackled the question how to extract this particular knowledge graph and how to evaluate its quality in a scalable manner.
+%In this work, we tackled the question how to extract this particular knowledge graph and how to evaluate its quality in a scalable manner.
 
@@
 % 1. No benchmark available -> we set up an evaluation framework based on textbooks and Wikipedia
-First, there was no classical benchmark available to evaluate the accuracy of extracted information.
+To conclude, our main contributions are the following.
+First, there is little research on how to evaluate the precision of extracted concept dependencies.
 Therefore, we propose a set of methods to use existing unstructured knowledge sources, namely Wikipedia and textbooks, to create baselines for evaluation.
 Due to the heuristic character of these methods, we conducted a manual assessment to test their suitability for our purpose.
-The resulting dataset can be used as a human baseline for further research.
+The resulting dataset can be used as a baseline for further research.
 
 % 2. Emerging field of prompt engineering -> we engineered a simple but effective prompt process to query a LLM
-Second, there is no established manner to extract the desired knowledge from the LLM.
-The emerging field of prompt engineering is currently a vast collection of commands to query LLMs.
-We propose a method called output refeeding that sequentially queries the language generation model and transforms its answers into a knowledge graph.
+Second, the emerging field of prompt engineering provides a constellation of commands to query LLMs, the majority of which are experimental and cannot be considered fully reliable.
+We propose a method called \textit{output refeeding} that allows mining the educational concept dependencies by sequentially querying the language generation model and transforming its answers into a knowledge graph.
 
@@
 % Cohen, 2023
+
+Multiple approaches of prompt engineering for graph creation have been recently developed. Few-shot prompting proved successful (\cite{cohen2023crawling})
+
 % GraphGPT
@@
 \subsection{Research design}
+
+Our research lies at the intersection of education sciences and computational linguistics that define the choice of methodology.
+On the one hand, we prompt a state-of-the-art large language model to build entity dependency graphs and evaluate its performance on the concept relations retrieved from Wikipedia and textbooks.
+On the other hand, we should ensure that the output is sound in terms of educational value, which requires additional qualitative assessment.
+
+Since no ground-truth knowledge graph exists and cannot be achieved in the field of education, we choose textbooks and Wikipedia as the baseline to be able to estimate the precision of the dependencies mined from the LLM.
+Each information extraction method is not fully independent of the other, in particular, entity recognition and concept disambiguation steps in the procedure for LLM and textbooks depend on Wikipedia.
+The evaluation was performed via 1) inspecting the output in the interactive dashboard, 2) manual labeling, and 3) convergence between the LLM and two baselines metric.
+
 % two baseline methods: textbooks and Wikipedia
@@
 \subsubsection{Wikipedia}
-% Why Wikipedia?
+% Why Wikipedia? % I asked ChatGPT :)
+
+Wikipedia is a valuable resource that has a good structure of concepts.
+One of the key factors that contribute to it is the use of a hierarchical structure.
+Articles are categorized into broader topics, and those topics are further divided into subtopics.
+This structure helps readers to navigate through the information in a logical and organized manner, allowing them to quickly find the information they need.
+Another factor is the use of hyperlinks to connect related articles.
+This allows readers to move seamlessly between articles and explore related concepts without having to leave the site or perform additional searches.
+Wikipedia also has a strong editorial process that ensures that articles are well-researched, well-written, and up-to-date.
+This process helps to maintain the quality and accuracy of the information presented on the site, which in turn helps to reinforce the logical structure of the concepts presented.
+
 % good coverage according to one of our papers
@@
 \subsubsection{Textbooks}
-% Types of textbooks (why linear algebra?)
+% Types of textbooks (why linear algebra?) % I asked ChatGPT :)
 
+We chose textbooks on linear algebra as they tend to have a good structure and order compared to other textbooks because linear algebra is a well-established and mature field of mathematics with a clear and logical progression of concepts.
+Moreover, linear algebra is used extensively in other fields, such as engineering, physics, and computer science.
+Therefore, many textbooks on linear algebra are written with the needs of these fields in mind, which helps to structure the content of the textbook in a clear and practical manner.
+Finally, the concepts in linear algebra are interrelated, and a strong understanding of earlier topics is often necessary to understand later topics.
+
+We used 10 books that are free and available online. 
 % Amount of data
@@
 % Wikifier: identify entity mentions using link targets and PageRank
-For preprocessing the textbooks we used Wikifier \citep{brank2017annotating}.
+First, the textbooks were converted from pdf format to raw texts and went through basic preprocessing.
+Then, Wikifier \citep{brank2017annotating} was exploited for entity recognition and disambiguation.
+
 % Wikisearch: query Wikipedia search engine for keyword (and field) and rank results based on Levenshtein distance
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=.95\textwidth]{img/dash_example.png}
+    \caption{A screenshot of the intercative application.}
+    \label{fig:dash_example}
+\end{figure}
+
 \subsection{Manual inspection via Dashboard}
-%
+We developed a Dashboard via graphing library for Python Plotly\footnote{https://plotly.com/python/} (Fig.\ref{fig:dash_example}).
+The application is devised so that one could examine the resulting graph itself in a convenient environment.
+It allows plotting the concept dependencies graphs for three knowledge sources or types of dependency mining methods (LLM, Wikipedia, and textbooks) for different levels of dependencies.
 
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.95\textwidth]{img/rating.pdf}
+    \caption{Rating.}
+    \label{fig:rating}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.4\textwidth]{img/kappa.pdf}
+    \caption{Interrater reliability, kappa coefficient.}
+    \label{fig:kappa}
+\end{figure}
+
 %Convergence statistics
 % diagram for similarity of outputs
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.95\textwidth]{img/comp_direct_deps.pdf}
+    \caption{Convergence metrics. Number of common direct dependencies between sources.}
+    \label{fig:comp_direct_deps}
+\end{figure}
 
@@
 % What are potential flaws?
+
 % disambiguation already includes noise
+% error propagation
+
 % we only evaluated up to two levels of the graph, not the graph as a whole. different level of abstractions in extracted dependencies
 % is there even something like a gold standard? some educational reflection about different didactic approaches and more depth than just understanding the definition of a topic
+% Cohen et al (2023) think that there is no gold standard, ground truth.
+
 % we are still using the language generator, so it is just another downstream task, maybe it is more of a philosophical question what is implicit/explicit knowledge
 
+% + "I don't know" option in the prompt engineering part
+% + Google search
+
 % Q: Outlook and Future research ideas:
+
+As shown, current LLMs are not sufficiently precise in creating concept maps, which confirms previous research \cite{hwang2021comet}.
+This could be improved by training the pre-trained models on the knowledge graph data mined from Wikipedia or any other reliable sources of concept dependencies in a specific subject of instruction \cite{west2022symbolic}.
 % advancements in LLMs that are interesting for us
@@
 
+\newpage
+
+\section{Appendix}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.95\textwidth]{img/comp_second_deps.pdf}
+    \caption{Convergence metrics. Number of common direct and second-level dependencies between sources.}
+    \label{fig:comp_second_deps}
+\end{figure}
+
 \end{document}

### 2023-03-09 doc/paper.tex
revise paper method section

@@
 
-This work tries to contribute to the research field and to answer the question of whether general LLMs are able to provide a valid dependency structure of educational concepts.
+This work contributes to this field and aims to answer the question of whether LLMs generally are able to provide a valid dependency structure of educational concepts.
 To find the answer to the research question, we are going to solve two main subtasks: 1) extraction of implicit educational concept dependencies, and 2) evaluation of the retrieved dependencies or the resulting graphs by existing knowledge media.
@@
 Within educational content, Merill (1983) differentiated facts, concepts, principles, rules, procedures, interpersonal skills, attitudes, and their sole recall from their application.
+% TODO: explain this more:
 We will focus on concepts and their relations defined understanding.
+
 % Concept dependency
@@
 % Other approaches: Learning Path Analysis and Expert Knowledge
-Prerequisites can be inferred from learner behavior by testing their performance after being presented different instructional sequences (Pavlik et al., 2008, Vuong et al., 2011).
+Prerequisites can be inferred from learner behavior by testing their performance after being presented with different instructional sequences (Pavlik et al., 2008, Vuong et al., 2011).
 However, this has the disadvantage of disengaging users with too difficult concepts before teaching easier or necessary ones.
@@
 \subsection{Research design} 
-
-Our research lies at the intersection of education sciences and computational linguistics that define the choice of methodology.
-On the one hand, we prompt a state-of-the-art large language model to build entity dependency graphs and evaluate its performance on the concept relations retrieved from Wikipedia and textbooks.
-On the other hand, we should ensure that the output is sound in terms of educational value, which requires additional qualitative assessment.
-
-Since no ground-truth knowledge graph exists and cannot be achieved in the field of education, we choose textbooks and Wikipedia as the baseline to be able to estimate the precision of the dependencies mined from the LLM.
-Each information extraction method is not fully independent of the other, in particular, entity recognition and concept disambiguation steps in the procedure for LLM and textbooks depend on Wikipedia.
-The evaluation was performed via 1) inspecting the output in the interactive dashboard, 2) manual labeling, and 3) convergence between the LLM and two baselines metric.
-
 % two baseline methods: textbooks and Wikipedia
@@
 % 3. convergence between LLM and baselines
+The choice of methodology reflects the fact that our research is located at the intersection of educational sciences and computational linguistics.
+On the one hand, we want to achieve a high performance of a state-of-the-art LLM in the downstream task of knowledge graph extraction.
+On the other hand, we consider a complex educational problem that cannot be purely simplified to classical machine learning metrics but requires additional qualitative assessment to ensure that our results can be educationally sound.
+
+First of all, we restricted the concepts, of which dependencies we assessed, to the domain of linear algebra.
+This design choice was caused by the assumptions that the highly structured domain of mathematics provides enough relations to capture on the one hand and that linear algebra is a rather matured branch of mathematics were enough data exists for our baselines to be created as well as the LLM to have learned about from its own training data.
+Due to the use of linear algebra in different disciplines the potential value of results is also increased.
+
+To be able to measure the LLM's performance, we had to come up with a target dataset.
+This dataset needs to describe a graph, containing the concepts as vertices and their dependencies as directed edges.
+Since no ground-truth, large-scale knowledge graph of concept dependencies was available to us and might even be impossible to achieve for our educational problem, we chose two sources of educational knowledge to serve as our knowledge base, namely textbooks, and Wikipedia.
+Due to their end-user-facing format, further processing of the input data (PDFs and webpages) was required to create the above-defined data structure.
+To make the graphs comparable with each other, the set of concepts was restricted to the union of all concepts indicated in all textbooks' indices.
+The LLM was prompted and the responses were also further processed to create the knowledge graph.
+
+After creating the baseline datasets and the output to evaluate, we started qualitative evaluation using an interactive dashboard, that visualized the dependency structure.
+This step was done to get an impression of the general suitability of all three pipelines and identify potential reasons for performance losses.
+Then a subset of all three datasets was manually rated by multiple raters to not only infer their overall quality but also assess the human performance on the problem.
+We finally checked for outputs for convergence to give suggestions for a scalable, low-cost evaluation system of future (versions of) LLMs.
+The former evaluations are rather typical in educational research whereas the latter enables the creation of large-scale datasets, potentially suitable to train and fine-tune machine learning models.
 
 \subsection{Baseline extraction}
+This section details how we used Wikipedia and textbooks to set up the evaluation baselines for the LLM.
+
 \subsubsection{Wikipedia}
-% Why Wikipedia? % I asked ChatGPT :)
+% Why Wikipedia? 
+The choice of the online encyclopedia Wikipedia as an educational information source is a result of its inherent graph structure induced by hyperlinks between articles and empirical evidence of its suitability for this purpose.
+%TODO: Add knowledge extraction literature from 2015/16
+Especially, the platform is claimed to cover concepts up to the complexity of undergraduate curricula to a high extent, which aligns well with our chosen domain of linear algebra, which is usually taught to undergraduate students.
+The focus on dependencies required for understanding a concept makes an encyclopedia an ideal source because its articles are usually written to enable a fast understanding of the article's topic.
+In an online encyclopedia, hyperlinks provide additional information.
+In Wikipedia, each content article begins with a short summary, often serving as a definition and embedding the topic into its context, before in-depth information follows.
+In this summary text, we assume an implicit order from most important to least important concepts that are used to explain the topic without digressing to other concepts or unimportant information.
+The involved concepts are inferred to be a dependency.
+To prevent direct cycles by two concepts involving each other in their explanation, the one that refers earlier to the other is considered to be dependent on the latter.
+Situations, where the introduction of concept A states that concept B is dependent on it might be resolved like this.
 
-Wikipedia is a valuable resource that has a good structure of concepts.
-One of the key factors that contribute to it is the use of a hierarchical structure.
-Articles are categorized into broader topics, and those topics are further divided into subtopics.
-This structure helps readers to navigate through the information in a logical and organized manner, allowing them to quickly find the information they need.
-Another factor is the use of hyperlinks to connect related articles.
-This allows readers to move seamlessly between articles and explore related concepts without having to leave the site or perform additional searches.
-Wikipedia also has a strong editorial process that ensures that articles are well-researched, well-written, and up-to-date.
-This process helps to maintain the quality and accuracy of the information presented on the site, which in turn helps to reinforce the logical structure of the concepts presented.
+Our assumptions about the Wikipedia structure were operationalized in the following way to compute the dependencies for a given concept.
+Every link in the first content paragraph containing a link is considered a candidate dependency.
+Therefore, any non-content paragraph such as advice regarding irrelevance or missing sources has to be removed beforehand.
+First, links to categories or fields such as "Mathematics" or "Linear Algebra" are removed based on a manually composed blacklist (a more sophisticated, automatic pruning could make use of Wikipedia's category pages).
+Then links to articles about persons are filtered out since these do not represent educational concepts.
+The same applies to links to pages that contain unexpected content such as disambiguation pages.
+Subsequently, cyclic dependencies are resolved as described above using both character positions of the symmetric links in the text.
+If more candidates remain than the threshold of 5, only the first 5 were kept, using the assumption of decreasing importance from the beginning on and the constraint of some sparsity of the resulting graph.
+This set of concepts is then taken as the concept's dependencies.
+%TODO: add amount of data
 
-% good coverage according to one of our papers
-% 1462 unique articles for book index entries, these were covered in the textbooks (we had to select a subset of concepts to reduce computational effort)
-% How did we get the information?
-% describe Algorithm to extract dependencies:
-%• Assumption: understanding the concept’s definition in Wikipedia requires understanding the concepts in it
-%• Operationalization: links to other articles in the first sentence of article
-%• Filtered out links to fields (“Mathematics”), persons (“Gabriel Cramer), and concepts that linked even earlier to the concept of interest
+The described procedure was executed for every concept in the set resulting from the textbook baseline.
+Although Wikipedia theoretically offers a larger number of articles about the topic, we decided to stick with the limited set to maintain comparability.
+However, we decided against restricting the dependencies to other concepts in the set to also be able to evaluate the recall of the methods.
+The computational complexity of the procedure is relatively low and most time is spent on requesting Wikipedia web pages for the concepts and the links.
+The overall time was hence reduced by caching the responses to these requests.
+The technical implementation in Python required engineering our own Wikipedia API using the Python libraries requests and BeautifulSoap.
+The tools are used to download the page content and conveniently access elements such as links or special HTML tags indicating that an article is about a person.
 
 \subsubsection{Textbooks}
-% Types of textbooks (why linear algebra?) % I asked ChatGPT :)
+% Why textbooks?
+We chose student textbooks as the complementary information source besides the general purpose knowledge base Wikipedia because they are written by experts specifically for the purpose of educational knowledge transfer to learners.
+This not only leads to comprehensive coverage of carefully selected concepts that are considered relevant by the authors but also to a specific structure that we planned to exploit with our baseline extraction method, namely a pedagogic linearization of topics.
+More precisely, the authors are expected to first introduce concepts that more complex concepts build upon.
+Another useful structure in textbooks is the index, which provides a comprehensive list of concepts covered in the book and defined as its own entities.
 
-We chose textbooks on linear algebra as they tend to have a good structure and order compared to other textbooks because linear algebra is a well-established and mature field of mathematics with a clear and logical progression of concepts.
-Moreover, linear algebra is used extensively in other fields, such as engineering, physics, and computer science.
-Therefore, many textbooks on linear algebra are written with the needs of these fields in mind, which helps to structure the content of the textbook in a clear and practical manner.
-Finally, the concepts in linear algebra are interrelated, and a strong understanding of earlier topics is often necessary to understand later topics.
-
-We used 10 books that are free and available online. 
 % Amount of data
-% 10 books on Linear Algebra
-% 584 pages on average (652,297 characters)
-% 382 number of index entries (median)
+Due to the popularity of the topic of Linear Algebra, we could easily identify ten free textbooks on the topic and obtain their PDF representations (either directly typeset in this format or scanned and processed with OCR).
+The books comprised 584 pages on average (652,297 characters) and had a median of 382 index entries.
 
@@
 % preprocessing
+
+% Wikisearch: query Wikipedia search engine for keyword (and field) and rank results based on Levenshtein distance
+First, the textbooks were converted from PDF format to unformatted text.
+To identify all concepts of interest covered in a book, the pages containing the index were identified and each index entry with its corresponding pages was extracted in a semi-manual fashion.
+This required setting parameters such as the title, position of the columns and the type of nesting.
+To enable comparing the knowledge graph across the baselines, we decided to use the set of Wikipedia articles as the set of concepts, meaning that only a Wikipedia article title can serve as a vertex.
+This required mapping from each index entry to the closest Wikipedia article.
+For this disambiguation, the term was introduced into the Wikipedia search engine suffixed with the field term "(Mathematics)" to hint to the general area.
+Due to the high diversity of the resulting 10 articles, their names were string-matched with the search term (without the suffix) using the Levenshtein distance (provided by a Python library).
+The article title with the lowest distance that did not refer to an disambiguation page was the result of this so-called \textit{Wikisearch disambiguation}.
+
+For the depdency extraction we came up with three distinct strategies.
+The first is solely based on indices whereas the latter also uses the full text.
+The first strategy is called order pruning and is interested in unlikely dependencies on the graph.
+It checks whether two concepts are introduced at least twice in a specific order and rules out the dependency that is not suggested by this order.
+For example if concept A is introduced twice before concept B, it is unlikely to depend on a concept introduced later by two independent authors.
+This strategy might work for a massive amount of books which was not available to us, but Wikifier \citep{brank2017annotating} was exploited for entity recognition and disambiguation.
+
+% relation extraction
+
 % entity recognition and disambigation
 % Wikifier: identify entity mentions using link targets and PageRank
-First, the textbooks were converted from pdf format to raw texts and went through basic preprocessing.
-Then, Wikifier \citep{brank2017annotating} was exploited for entity recognition and disambiguation.
-
-% Wikisearch: query Wikipedia search engine for keyword (and field) and rank results based on Levenshtein distance
-
-% relation extraction
 % common introductory usage: identify other concepts that are most often mentioned on the first page given in the index across all books
 % order pruning:  identify unlikely dependencies based on a certain number of books that introduce concepts in a particular order
+
+We used 10 books that are free and available online.
 
@@
 % we only evaluated up to two levels of the graph, not the graph as a whole. different level of abstractions in extracted dependencies
+% (in)direct cycles
 % is there even something like a gold standard? some educational reflection about different didactic approaches and more depth than just understanding the definition of a topic
 % Cohen et al (2023) think that there is no gold standard, ground truth.
+
+Each information extraction method is not fully independent of the other, in particular, entity recognition and concept disambiguation steps in the procedure for LLM and textbooks depend on Wikipedia.
 

### 2023-03-10 doc/paper.tex
revise paper and add slides

@@
 We chose student textbooks as the complementary information source besides the general purpose knowledge base Wikipedia because they are written by experts specifically for the purpose of educational knowledge transfer to learners.
-This not only leads to comprehensive coverage of carefully selected concepts that are considered relevant by the authors but also to a specific structure that we planned to exploit with our baseline extraction method, namely a pedagogic linearization of topics.
-More precisely, the authors are expected to first introduce concepts that more complex concepts build upon.
-Another useful structure in textbooks is the index, which provides a comprehensive list of concepts covered in the book and defined as its own entities.
+This does not only lead to comprehensive coverage of carefully selected concepts that are considered relevant by the authors but also to a specific structure that we planned to exploit with our baseline extraction method, namely a pedagogic linearization of topics.
+More precisely, the authors are expected to first introduce concepts that other more complex concepts build upon.
+Another useful structure in textbooks is the index, which provides a comprehensive list of concepts defined as its own entities and covered in the book, and indicates the area of introduction.
 
 % Amount of data
-Due to the popularity of the topic of Linear Algebra, we could easily identify ten free textbooks on the topic and obtain their PDF representations (either directly typeset in this format or scanned and processed with OCR).
-The books comprised 584 pages on average (652,297 characters) and had a median of 382 index entries.
+Due to the popularity of the topic of Linear Algebra, we could easily identify ten free textbooks on the topic and obtain their PDF representations (either directly typeset in this format or scanned and processed with optical character recognition).
+The books comprised 584 pages on average (652,297 characters) and disposed of a median of 382 index entries.
 
@@
 To identify all concepts of interest covered in a book, the pages containing the index were identified and each index entry with its corresponding pages was extracted in a semi-manual fashion.
-This required setting parameters such as the title, position of the columns and the type of nesting.
-To enable comparing the knowledge graph across the baselines, we decided to use the set of Wikipedia articles as the set of concepts, meaning that only a Wikipedia article title can serve as a vertex.
-This required mapping from each index entry to the closest Wikipedia article.
-For this disambiguation, the term was introduced into the Wikipedia search engine suffixed with the field term "(Mathematics)" to hint to the general area.
-Due to the high diversity of the resulting 10 articles, their names were string-matched with the search term (without the suffix) using the Levenshtein distance (provided by a Python library).
-The article title with the lowest distance that did not refer to an disambiguation page was the result of this so-called \textit{Wikisearch disambiguation}.
-
-For the depdency extraction we came up with three distinct strategies.
-The first is solely based on indices whereas the latter also uses the full text.
-The first strategy is called order pruning and is interested in unlikely dependencies on the graph.
-It checks whether two concepts are introduced at least twice in a specific order and rules out the dependency that is not suggested by this order.
-For example if concept A is introduced twice before concept B, it is unlikely to depend on a concept introduced later by two independent authors.
-This strategy might work for a massive amount of books which was not available to us, but Wikifier \citep{brank2017annotating} was exploited for entity recognition and disambiguation.
+This required setting parameters such as the title, position of the text columns, and the types of nesting and delimiters.
+To enable comparing the knowledge graph across the baselines, we decided to use the set of Wikipedia articles as the set of possible concepts, meaning that only a Wikipedia article title can serve as a vertex in the knowledge graph.
+This required to map from each index entry to the closest Wikipedia article.
+For this disambiguation, the index entry was introduced into the Wikipedia search engine suffixed with the field term "(Mathematics)" to hint at the general area.
+Due to the high diversity of the resulting ten articles, their titles were string-matched with the search term (excluding the suffix) using the Levenshtein distance (provided by a Python library).
+The article title with the lowest Levenshtein distance that did not refer to a disambiguation page was the result of this so-called \textit{Wikisearch disambiguation}.
 
@@
 % entity recognition and disambigation
+For dependency extraction, we came up with two distinct strategies.
+% order pruning:  identify unlikely dependencies based on a certain number of books that introduce concepts in a particular order
+The first is solely based on indices whereas the latter also uses the full text.
+The first strategy is called \textit{order pruning} and is focused on unlikely dependencies on the graph.
+It checks whether two concepts are introduced at least twice in a specific order and rules out the dependency that is not suggested by this order.
+For example, if concept A is introduced twice before concept B, it is unlikely to depend on a concept introduced later by two independent authors.
+To create a sparse graph, this strategy requires a massive amount of books, which was not available to us, but it can help to prune dependencies and refine a candidate graph.
+
+% common introductory usage: identify other concepts that are most often mentioned on the first page given in the index across all books
+This candidate graph is the output of the second heuristic called \textit{common introductory usage}.
+This is based on a similar rationale as the Wikipedia heuristic because it figures out which other concepts are used to introduce a new concept.
+The first and rather structured source of information is the index, again.
+Some books list multiple pages for index entries, indicating that the concept occurs again at a later point in a significant way.
+If concept A appears for the second time on the first page for concept B, A is likely to be a dependency of B.
+However, the structured source of index entries has a low amount of data, which led to the involvement of the full text.
+Here, entity recognition plays a crucial role because not every word is a concept of interest and not every concept occurs with its canonical title in natural text.
+
 % Wikifier: identify entity mentions using link targets and PageRank
-% common introductory usage: identify other concepts that are most often mentioned on the first page given in the index across all books
-% order pruning:  identify unlikely dependencies based on a certain number of books that introduce concepts in a particular order
+One convenient method is provided by the Wikifier \citep{brank2017annotating}.
+The underlying algorithm looks for links in the entire Wikipedia with the link text matching a word in the input.
+Naturally, the same text can link to distinct articles, which requires disambiguation based on the context.
+Wikifier solves this by creating a graph based on all potential links and uses a PageRank algorithm to calculate the score for each potential link target.
+We restricted links to correspond to a link text of at least 3 characters to get rid of abbreviations that were contained in formulas randomly.
+We used a minimum PageRank of 0.00005 as a threshold after manual inspection aimed at a good recall of links but also good precision.
+The Wikifier was called via its online API.
+All detected link targets on the first page of an index entry serve as candidate dependencies which are then ranked by the following three criteria: First, the number of books in which it occurs in the area of introduction.
+Second, the average number of occurrences in these books.
+Third, the PageRank of the link.
+As with the Wikipedia dependencies, only the 5 highest-ranking candidates are saved as dependencies in the knowledge graph.
+This procedure was carried out for all index entries across all books.
 
-We used 10 books that are free and available online.
+The final resulting graph is the union of dependencies identified by the two common introductory usage sources (indices and full text), pruned by the unlikely dependencies from order pruning.
 
@@
 % • Fine-tuned BLOOM on several question-answering datasets
-% • 11 billion parameters (44GB RAM) • ~3-10 seconds per request on our infrastructure
+% • 11 billion parameters () • ~3-10 seconds per request on our infrastructure
+Due to the closed-source character of the very powerful and successful language model GPT3 by openai and the unavailability of an API for its most recent application ChatGPT, we decided to use the open-source model BLOOM by bigscience, which is a joint effort by hundreds of researchers around the world and is based on the same transformers architecture as GPT3 and has a comparable amount of parameters.
+Because of resource limitations and our specific use case, we used a derived model called \textit{T0pp} (https://huggingface.co/bigscience/T0pp), which only has 11 billion parameters and is fine-tuned for zero-shot task generalization, especially question-answering.
+The dataset used for training T0pp is also available under the name P3 (Public Pool of Prompts) (https://huggingface.co/datasets/bigscience/P3).
+We set up the language model on the cloud infrastructure of the university's excellence cluster and ran it in generation mode (no training) with a maximum response length of 50 tokens on a node with eight cores of the type Nvidia GeForce RTX 2080 Ti.
+This model consumed approximately 44GB of RAM and a typical request took three to ten seconds to be answered completely.
+To save time loading the model into the memory, we set up an HTTP server to conveniently query the model via GET requests from our local machines.
 
-% description of extraction procedure
+% description of the extraction procedure
 % 1. output refeeding
@@
 % {canonical list of dependencies} :=Wikisearch disambiguation on {list of dependencies}
+Manual trial and error testing of our chosen and other LLMs (such as meta's Galactica) has led to the following procedure to extract dependencies from the knowledge base of T0pp, which we call \textit{output refeeding}.
+It is based on the previously explained assumption that understanding a concept requires understanding other concepts involved in its definition.
+Given a concept of interest, we therefore first prompt the model for a definition of the concept: "What is the mathematical definition of {concept}?" The response is defined as {definition} and involved in the second prompt: "What mathematical concepts are mentioned here: {definition}".
+The model usually responds with a comma-separated list that is split by commas and then disambiguated in the same way as the index entries in the textbook baseline by our Wikisearch disambiguation.
+Finally, self-dependencies, that might occur during this procedure, are deleted from the set of dependencies.
+This procedure is run for the same set of concepts as the Wikipedia baseline.
 
@@
     \includegraphics[width=.95\textwidth]{img/dash_example.png}
-    \caption{A screenshot of the intercative application.}
+    \caption{A screenshot of the interactive application.}
     \label{fig:dash_example}
@@
 \subsection{Manual inspection via Dashboard}
-We developed a Dashboard via graphing library for Python Plotly\footnote{https://plotly.com/python/} (Fig.\ref{fig:dash_example}).
+As indicated in our design, this educational problem requires also a qualitative evaluation.
+We hence developed a Dashboard via graphing library for Python Plotly\footnote{https://plotly.com/python/} (Fig.\ref{fig:dash_example}).
 The application is devised so that one could examine the resulting graph itself in a convenient environment.
-It allows plotting the concept dependencies graphs for three knowledge sources or types of dependency mining methods (LLM, Wikipedia, and textbooks) for different levels of dependencies.
+It allows plotting the concept dependencies graphs for three knowledge sources and types of dependency mining methods (LLM, Wikipedia, and textbooks) for different depths of dependencies, meaning that dependencies of dependencies are shown.
+The dashboard also has potential use for educators that are interested in concept dependencies.
 
@@
 % procedure to assess the accuracy of output
+The novel character of our baselines and the resulting uncertainty about their appropriateness to evaluate the LLM's performance motivated us to evaluate all three knowledge graphs independently before checking their convergence.
+Therefore, 4 raters were presented with 100 dependencies from each graph and had to rate them in a binary fashion (correct vs incorrect).
+We only evaluated the quality of dependencies for concepts that occurred at least in 50\% of the textbooks to ensure that there is enough data for the textbook baseline and that we assess the data for important concepts only.
+For the ratings, we calculated Cohen's Kappa as a measure of interrater reliability.
+This should not only guarantee the confidence of the performance evaluation but also assess the difficulty of the problems for human raters.
 
-\subsection{Convergence statistics}
+\subsection{Baseline consistency}
 % for which concepts did we compare what to see what
+Consistency of the LLM with the baselines is the most scalable measure because the baselines can be mostly created automatically and hence be used to evaluate large numbers of LLM outputs or even fine-tune the model for this specific downstream task.
+First-order consistency is fulfilled for a concept dependency extracted from the LLM if it is a direct dependency for this concept also in the baseline.
+Second-order consistency is fulfilled
 
@@
 
+\section{Acknowledgements}
+We sincerely thank our project supervisors, Álvaro Tejero-Cantero and Hanqi Zhou.
+
 \bibliography{references.bib}

### 2023-03-13 doc/paper.tex
update paper

@@
 \usepackage[preprint]{neurips_2021}
+\usepackage{setspace}
+\onehalfspacing
 
@@
 
-\title{Extracting and evaluating educational concept dependencies from Large Language Models}
+\title{Extracting and evaluating concept dependencies from Large Language Models}
 
@@
 % lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
-% authors names on the first line, and the last on the second line, try using
+% authors' names on the first line, and the last on the second line, try using
 % \AND instead of \And before the third author name.
@@
 
-% Why did we to it? What did we expect?
+% Why did we do it? What did we expect?
 
@@
 % Field of contribution
-Large Language Models (LLMs) are trained on immense corpora of text and have proven to build on embedded factual information when performing well in downstream tasks such as question answering.
-Accessing this knowledge, which is represented by billions of parameters and the network's architecture, has given rise to the research field of Knowledge Extraction from LLMs (\cite{cohen2023crawling}), which rests on the assumption that the language models can help retrieve information on the relation between entities.
-
-This work contributes to this field and aims to answer the question of whether LLMs generally are able to provide a valid dependency structure of educational concepts.
-To find the answer to the research question, we are going to solve two main subtasks: 1) extraction of implicit educational concept dependencies, and 2) evaluation of the retrieved dependencies or the resulting graphs by existing knowledge media.
-
-Apart from the field of knowledge extraction from LLMs, which is a subfield of computational linguistics, our work may contribute to applied education sciences by improving computer-assisted education and creating new perspectives for a subfield of knowledge engineering that has rather stagnated in the previous years.
+Large Language Models (LLMs) are trained on immense corpora of text and build on included factual information when performing well in downstream tasks such as question answering.
+Accessing this knowledge, which is represented by billions of parameters and the network's architecture, has given rise to the research field of Knowledge Extraction from LLMs \citep{cohen2023crawling}, which rests on the assumption that the language models can help retrieve information on the relation between entities.
+This work contributes to the field and addresses the question of whether LLMs can provide a precise dependency structure of concepts.
+Apart from the field of knowledge extraction from LLMs, part of computational linguistics, our work contributes to applied education sciences by providing data for computer-assisted education and creating new perspectives for educational knowledge engineering.
 
@@
 %% Problem of sequencing in Instructional Design:
-In particular, effective and efficient instruction does not only incorporate what to teach but also how to teach, especially the order of instruction.
-It is proven that \textit{instructional sequencing} enhances the process of learning when prerequisites of educational content are known to the student or taught first \citep{morrison2019designing}.
+Effective and efficient instruction does not only incorporate what to teach but also how to teach it, especially the order of instruction.
+The empirically proven theory of \textit{Instructional Sequencing} states that prior knowledge of prerequisite learning content or previous exposure to it enhances learning \citep{morrison2019designing}.
 % Definition concepts
-Within educational content, Merill (1983) differentiated facts, concepts, principles, rules, procedures, interpersonal skills, attitudes, and their sole recall from their application.
+Within learning contents, \cite{merrill1983component} differentiated facts, concepts, principles, rules, procedures, interpersonal skills, attitudes, and their sole recall from their application.
 % TODO: explain this more:
-We will focus on concepts and their relations defined understanding.
-
+For simplicity, we focus only on concepts such as the "Pythagorean Theorem", which could be a topic for a lecture or a (sub)chapter in a textbook, and do not distinguish between recall and application.
 % Concept dependency
 % Assumption: information about dependencies between concepts makes instructional sequencing more effective in terms of learning
-
-To be more precise, if one concept is a prerequisite of another, we refer to this relation as a concept dependency.
-For example, to understand the concept of a derivative, having knowledge about the concept of a function will facilitate or even enable learning.
-When the dependencies are thought of as directed edges between nodes that represent concepts, a concept dependency graph emerges which is a special type of a knowledge graph \citep{wang2016using}.
+To be more precise, if one concept is a prerequisite of another, we refer to this relation as a \textit{concept dependency}.
+For example, to understand the concept of a derivative, knowing the concept of a function will facilitate or even enable learning.
+Importantly, the dependency relation is distinguished from the similarity, hierarchy, and reference relation \citep{gordon-etal-2016-modeling}.
+Besides that, the terms prerequisite and concept dependency are used interchangeably.
+When the concepts are thought of as nodes and the dependencies as directed edges between them, a concept dependency graph emerges, a special type of knowledge graph \citep{wang2016using}.
 This graph is also called \textit{concept map} in the field of Learning Sciences.
 % TODO: provide a (graphical) example of a small concept map
-% Why is is important?
-The graph can be used to advance curriculum planning (\cite{yang2015concept}), especially for new topics that might not be covered in textbooks or automated assessment (Wang, 2015).
+% Why is it important?
+The graph can be used to generate ordered reading lists \citep{gordon-etal-2016-modeling}, and hence advance curriculum planning \citep{yang2015concept}, especially for new topics that might not be covered in existing courses.
+Another use case is automated assessment, where the dependencies can increase the meaning of performance in a task because this can indicate skills in its dependencies \citep{wang2016using}.
 
-% What is the gap in research that we tackle?
 % What is our research question?
-% How to extract educational concept dependencies that are implicit and evaluate them using existing knowledge media?
-%In this work, we tackled the question how to extract this particular knowledge graph and how to evaluate its quality in a scalable manner.
-
-% What can we contribute?
+% How to extract educational concept dependencies that are implicit and evaluate them using existing knowledge sources?
+In this work, we tackled the question of how to extract this particular knowledge graph and how to evaluate its quality in a scalable manner.
+% What can we contribute/which gap do we sholve?
 % 1. No benchmark available -> we set up an evaluation framework based on textbooks and Wikipedia
-To conclude, our main contributions are the following.
-First, there is little research on how to evaluate the precision of extracted concept dependencies.
-Therefore, we propose a set of methods to use existing unstructured knowledge sources, namely Wikipedia and textbooks, to create baselines for evaluation.
+Our main contributions are the following:
+First, there is little research on how to automatically evaluate the precision of extracted concept dependencies, which can be used to train and fine-tune models for this task.
+Therefore, we propose a set of methods to create baselines for evaluation from two existing unstructured knowledge sources, namely Wikipedia and textbooks.
 Due to the heuristic character of these methods, we conducted a manual assessment to test their suitability for our purpose.
 The resulting dataset can be used as a baseline for further research.
-
-% 2. Emerging field of prompt engineering -> we engineered a simple but effective prompt process to query a LLM
+% 2. The emerging field of prompt engineering -> we engineered a simple but effective prompt process to query an LLM
 Second, the emerging field of prompt engineering provides a constellation of commands to query LLMs, the majority of which are experimental and cannot be considered fully reliable.
@@
 \cite{talukdar2012crowdsourced} defined the prerequisite relation in terms of the consumption of information about concepts.
-Vuong (2011) if a better graduation rate given prerequisite knowledge is fulfilled.
-Concepts are often equated with Wikipedia articles (Talukdar and Cohen, 2012; Wang, 2015).
+This coincides with the operationalization of a concept dependency by \cite{gordon-etal-2016-modeling}, who defined it in terms of the helpfulness of learning about another concept and their modeling of information flow to determine the relation.
+\cite{vuong2011method} defined the relation in terms of performance.
+More specifically, prior knowledge that leads to a better graduation rate is considered a prerequisite.
+Concepts are often equated with Wikipedia articles \citep{wang2016prerequisite} but also with results of topic modeling \citep{gordon-etal-2016-modeling}.
 
-% Other approaches: Learning Path Analysis and Expert Knowledge
-Prerequisites can be inferred from learner behavior by testing their performance after being presented with different instructional sequences (Pavlik et al., 2008, Vuong et al., 2011).
-However, this has the disadvantage of disengaging users with too difficult concepts before teaching easier or necessary ones.
-Experts usually dispose of the required knowledge about concepts to create concept maps.
-The high cost of expert knowledge motivates the automated extraction of concept dependencies from appropriate sources.
+% of interest: How are relationships between concepts extracted?
+\cite{gordon-etal-2016-modeling} presented two information theoric approaches to extract the dependency relation from a corpus of scientific documents, in which concepts were obtained by a topic model and filtered by human judges.
+Their entropy-based approach predicts a dependency of concept A on concept B to the extent that the distribution of B can predict the distribution of A.
+Their information flow approach is also based on co-occurrences of topics in documents but simulates navigation through the documents and considers transitions to documents about other topics as dependencies.
+Word similarity, citations, and hierarchy served as baselines where word similarity performed better or equally well as the proposed approaches in terms of precision and recall, indicating that their modeled relation is rather symmetric and hence not helpful for sequential curriculum planning.
 
-% Field: Textbook Knowledge Extraction
-% of interest: How are relationships betweens concepts extracted?
+\cite{liang2015measuring} defined the reference distance metric (RefD) that reflects the extent to which concepts related to concept A (for example by hyperlinks) refer to concepts related to concept B compared to vice versa.
+If concepts related to A do this more strongly than the other way around, concept A is considered dependent on B.
+Their proposed measures on Wikipedia concepts performed better than the MaxEntropy classifier on the CrowdComp dataset by \cite{talukdar2012crowdsourced} and their Courses dataset.
 
+More recent approaches already involved neural networks.
+\cite{gasparetti2022discovering} fed embeddings for the concepts into a number of popular binary classifiers and outperformed the previously referenced methods.
+\cite{sun2022conlearn} also worked with concept embeddings but feed them together with a concept dependency graph into a graph neural network to predict the dependency structure between concepts.
 % Field: Prompt Engineering for Knowledge Graph creation
@@
 % Cohen, 2023 
+Multiple approaches of prompt engineering for graph creation have been recently developed. Few-shot prompting proved successful \citep{cohen2023crawling}.
+% GraphGPT
 
-Multiple approaches of prompt engineering for graph creation have been recently developed. Few-shot prompting proved successful (\cite{cohen2023crawling})
-
-% GraphGPT
+% Other approaches: Learning Path Analysis and Expert Knowledge
+Prerequisites can be also behaviorally inferred from learning paths by testing learners' performance after being presented with different instructional sequences \citep{pavlik2008using,vuong2011method} or analyzing human navigation through information sources \citep{gordon-etal-2016-modeling}.
+However, these approaches usually lack data, and creating this data has the disadvantage of disengaging users with too difficult concepts before teaching easier or more necessary ones.
+Experts usually dispose of the required knowledge about concepts to create concept maps.
+The high cost of expert knowledge motivates the automated extraction of concept dependencies.
 
@@
 % 3. convergence between LLM and baselines
-The choice of methodology reflects the fact that our research is located at the intersection of educational sciences and computational linguistics.
+The choice of methodology reflects the fact that our research is located at the intersection of education sciences and computational linguistics.
 On the one hand, we want to achieve a high performance of a state-of-the-art LLM in the downstream task of knowledge graph extraction.
@@
 First of all, we restricted the concepts, of which dependencies we assessed, to the domain of linear algebra.
-This design choice was caused by the assumptions that the highly structured domain of mathematics provides enough relations to capture on the one hand and that linear algebra is a rather matured branch of mathematics were enough data exists for our baselines to be created as well as the LLM to have learned about from its own training data.
-Due to the use of linear algebra in different disciplines the potential value of results is also increased.
+This design choice was caused by the assumptions that the highly structured domain of mathematics provides enough relations to capture on the one hand and that linear algebra is a rather mature branch of mathematics where enough data exists for our baselines to be created as well as the LLM to have learned about from its training data.
+Due to the use of linear algebra in different disciplines, the potential value of results is also increased.
 
@@
 To make the graphs comparable with each other, the set of concepts was restricted to the union of all concepts indicated in all textbooks' indices.
-The LLM was prompted and the responses were also further processed to create the knowledge graph.
+The LLM was prompted and the responses were also further processed to create a knowledge graph.
 
@@
 We finally checked for outputs for convergence to give suggestions for a scalable, low-cost evaluation system of future (versions of) LLMs.
-The former evaluations are rather typical in educational research whereas the latter enables the creation of large-scale datasets, potentially suitable to train and fine-tune machine learning models.
+The former evaluations are rather typical in education research whereas the latter enables the creation of large-scale datasets, potentially suitable to train and fine-tune machine learning models.
 
@@
 % Why Wikipedia? 
-The choice of the online encyclopedia Wikipedia as an educational information source is a result of its inherent graph structure induced by hyperlinks between articles and empirical evidence of its suitability for this purpose.
-%TODO: Add knowledge extraction literature from 2015/16
-Especially, the platform is claimed to cover concepts up to the complexity of undergraduate curricula to a high extent, which aligns well with our chosen domain of linear algebra, which is usually taught to undergraduate students.
+The choice of the online encyclopedia Wikipedia as an educational information source is a result of its inherent graph structure induced by hyperlinks between articles and empirical evidence of its suitability for this purpose \citep{wang2016prerequisite}.
+Especially, the platform is claimed to cover concepts up to the complexity of undergraduate curricula to a high extent, which aligns well with our chosen domain of linear algebra, which is usually taught to undergraduate students \citep{yang2015concept}.
 The focus on dependencies required for understanding a concept makes an encyclopedia an ideal source because its articles are usually written to enable a fast understanding of the article's topic.
 In an online encyclopedia, hyperlinks provide additional information.
-In Wikipedia, each content article begins with a short summary, often serving as a definition and embedding the topic into its context, before in-depth information follows.
+In Wikipedia, each content article begins with a summary, often serving as a definition and embedding the topic into its context, before in-depth information follows.
 In this summary text, we assume an implicit order from most important to least important concepts that are used to explain the topic without digressing to other concepts or unimportant information.
@@
 This set of concepts is then taken as the concept's dependencies.
-%TODO: add amount of data
+%TODO: add the amount of data
 
@@
 Although Wikipedia theoretically offers a larger number of articles about the topic, we decided to stick with the limited set to maintain comparability.
-However, we decided against restricting the dependencies to other concepts in the set to also be able to evaluate the recall of the methods.
+However, we decided against restricting the dependencies to concepts in the set to also be able to evaluate the recall of the methods.
+% TODO: recall?
 The computational complexity of the procedure is relatively low and most time is spent on requesting Wikipedia web pages for the concepts and the links.
 The overall time was hence reduced by caching the responses to these requests.
-The technical implementation in Python required engineering our own Wikipedia API using the Python libraries requests and BeautifulSoap.
+The technical implementation in Python required engineering our own Wikipedia API using the libraries requests and BeautifulSoap.
 The tools are used to download the page content and conveniently access elements such as links or special HTML tags indicating that an article is about a person.
@@
 % Why textbooks?
-We chose student textbooks as the complementary information source besides the general purpose knowledge base Wikipedia because they are written by experts specifically for the purpose of educational knowledge transfer to learners.
-This does not only lead to comprehensive coverage of carefully selected concepts that are considered relevant by the authors but also to a specific structure that we planned to exploit with our baseline extraction method, namely a pedagogic linearization of topics.
-More precisely, the authors are expected to first introduce concepts that other more complex concepts build upon.
-Another useful structure in textbooks is the index, which provides a comprehensive list of concepts defined as its own entities and covered in the book, and indicates the area of introduction.
+We chose student textbooks as the complementary information source besides the general purpose knowledge base Wikipedia because they are written by experts specifically for educational knowledge transfer to learners.
+This does not only lead to comprehensive coverage of carefully selected concepts that are considered relevant by the authors but also to a specific structure that our baseline extraction method exploits, namely a didactic linearization of topics.
+More precisely, the authors are expected to first introduce concepts that later introduced concepts build upon.
+Another useful structure in textbooks is the index, which provides a comprehensive list of concepts defined as its entities and covered in the book, and indicates the area of introduction.
 
@@
 % Wikisearch: query Wikipedia search engine for keyword (and field) and rank results based on Levenshtein distance
-First, the textbooks were converted from PDF format to unformatted text.
+First, the textbooks were converted from PDF to unformatted text.
 To identify all concepts of interest covered in a book, the pages containing the index were identified and each index entry with its corresponding pages was extracted in a semi-manual fashion.
@@
 
-% entity recognition and disambigation
+% entity recognition and disambiguation
 For dependency extraction, we came up with two distinct strategies.
@@
 % {canonical list of dependencies} :=Wikisearch disambiguation on {list of dependencies}
-Manual trial and error testing of our chosen and other LLMs (such as meta's Galactica) has led to the following procedure to extract dependencies from the knowledge base of T0pp, which we call \textit{output refeeding}.
+Manual inspection of our chosen and other LLMs' responses (such as meta's Galactica) has led to the following procedure to extract dependencies from the knowledge base of T0pp, which we call \textit{output refeeding}.
 It is based on the previously explained assumption that understanding a concept requires understanding other concepts involved in its definition.
@@
 \subsection{Manual baseline}
-% procedure to assess the accuracy of output
+% procedure to assess the accuracy of the output
 The novel character of our baselines and the resulting uncertainty about their appropriateness to evaluate the LLM's performance motivated us to evaluate all three knowledge graphs independently before checking their convergence.
@@
 % for which concepts did we compare what to see what
-Consistency of the LLM with the baselines is the most scalable measure because the baselines can be mostly created automatically and hence be used to evaluate large numbers of LLM outputs or even fine-tune the model for this specific downstream task.
+Consistency of the LLM with the baselines is the most scalable measure because the baselines can be created automatically and hence be used to evaluate large numbers of LLM outputs or even fine-tune the model for this specific downstream task.
 First-order consistency is fulfilled for a concept dependency extracted from the LLM if it is a direct dependency for this concept also in the baseline.
-Second-order consistency is fulfilled
+Second-order consistency is fulfilled if a dependency is among the direct dependencies or the dependencies of dependencies in the baseline.
+We are interested in the relative number of consistent dependencies between the LLM and the baseline because this gives an estimate of the precision of the predictions.
+However, it is also helpful to measure the recall by calculating the relative number of baseline dependencies that were correctly guessed.
+In the first-order consistency, this is just a change in the denominator.
 
@@
 % What is our main result?
-% we are able to make the implicit knowledge explicit far above chance level
+% we can make the implicit knowledge explicit far above chance level
 % problem is very complex -> humans do not fully agree
@@
 
-% we only evaluated up to two levels of the graph, not the graph as a whole. different level of abstractions in extracted dependencies
+% we only evaluated up to two levels of the graph, not the graph as a whole. different levels of abstractions in extracted dependencies
 % (in)direct cycles
 % is there even something like a gold standard? some educational reflection about different didactic approaches and more depth than just understanding the definition of a topic
-% Cohen et al (2023) think that there is no gold standard, ground truth.
+% Cohen et al (2023) think that there is no gold standard or ground truth.
 
